Collaboratively Testing the Validity of Neuroscientific Models

### 2013-11-30 NeurounitFrontiers/Paper.tex
Revised example script and added reference to bib

\documentclass{frontiersSCNS}
%\documentclass{article}
%\usepackage{biblatex}
%\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage{times}
\usepackage{hyperref}
%\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{listings}
%\usepackage[usenames,dvipsnames]{xcolor}
%\usepackage{setspace}
\usepackage{python_syntax}
%\usepackage{bibentry}
\usepackage{todonotes}
\usepackage{url}
\usepackage{lineno}
%\usepackage{natbib}
%\usepackage{caption}

@@

\subsection{Reference Data for Tests from NeuroElectro}\label{sec:neuroelectro} 
\begin{figure}
\begin{python}
# Interface with neuroelectro.org to search for spike widths of CA1 Pyramidal cells. 
reference_data = neuroelectro.NeuroElectroSummary(
  neuron = {'name':'Hippocampus CA1 pyramidal cell'}, # Neuron type.  
  ephysprop = {'name':'Spike Width'}) # Electrophysiological property name.
reference_data.get_values()  # Get summary data for the above. 
model = CA1PyramidalCellModel(population_name="CG_CML_0") # Initialize the model with some parameters.
test = SpikeWidthTestDynamic( # Initialize the test.    
	reference_data = {'mean':reference_data.mean, 'std':reference_data.std}, # Summary statistics from the reference data
	model_args = {'current':40.0}, # Somatic current injection in pA.  
	comparator = ZComparator), # A comparison class that implements a Z-score.  
result = sciunit.judge(test,model) # (1) Check capabilities, (2) take the test, (3) generate a score and validate it, (4) bind the score to model/test combination. 
result.summarize() # Summarize the result.  
\end{python}
\vspace{-15px}
\caption{Working example of testing in \textit{NeuronUnit}}
\label{fig:neuronunit_example}

@@

\subsection{A Complete Pipeline}
Although the tools described in Sec. \ref{sec:neuronunit} do not exhaust the possible sources of models, capabilities, and test data, they provide an immediate point of entry into the neurophysiology community and a powerful demonstration of our proposal. 
In the \textit{NeuronUnit} repository (\url{http://github.com/scidash/neuronunit}) is a runnable script (\textit{examples.py}) demonstrating a complete testing pipeline. 
It (1) selects an OSB model; 
(2) simulates it using NeuroConstruct; 
(3) tests the widths of the resulting action potentials, extracted and computed using NeuroTools, against NeuroElectro data downloaded on-the-fly, using a \textit{NeuronUnit} test class called \verbx{SpikeWidthTestDynamic}; \todo{Update this with current examples.py content, and changed to ipython notebook notation}
and (4) computes and prints a test score (Figure~\ref{fig:neuronunit_example}).

>>>>

\documentclass{frontiersSCNS}
%\documentclass{article}
%\usepackage{biblatex}
%\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage{times}
\usepackage{hyperref}
%\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{listings}
%\usepackage[usenames,dvipsnames]{xcolor}
%\usepackage{setspace}
\usepackage{python_syntax}
%\usepackage{bibentry}
\usepackage{todonotes}
\usepackage{url}
\usepackage{lineno}
\usepackage{upquote}
%\usepackage{natbib}
%\usepackage{caption}

@@

\subsection{Reference Data for Tests from NeuroElectro}\label{sec:neuroelectro} 
\begin{figure}
\begin{python}
reference_data = neuroelectro.NeuroElectroSummary( # Pooled experimental data from  neuroelectro.org. 
  neuron = {'name':'Hippocampus CA1 pyramidal cell'}, # Neuron type according to NeuroLex ontology.  
  ephysprop = {'name':'Spike Width'}) # Electrophysiological property name in same.
reference_data.get_values()  # Get summary data for the above. 
model = models.OSBModel( # Initialize the model.
        'hippocampus', # Brain area.  
        'CA1_pyramidal_neuron', # Neuron type name in OSB.  
        'CA1PyramidalCell') # Model name (Migliore et al, 2005).
test = SpikeWidthTest( # Initialize the test.    
	reference_data = {'mean':reference_data.mean, 'std':reference_data.std}, # Summary statistics.
	model_args = {'current':40.0*pA}, # Somatic current injection in pA.  
	comparator = ZComparator), # A comparison class that implements a Z-score.  
record = test.judge(model) # (1) Check capabilities, (2) take the test, (3) generate a score and validate it, (4) bind the score to model/test combination. 
record.summarize() # Summarize the result.  
\end{python}
\vspace{-15px}
\caption{Working example of testing in \textit{NeuronUnit}. Imports excluded for clarity.}
\label{fig:neuronunit_example}

@@

\subsection{A Complete Pipeline}
Although the tools described in Sec. \ref{sec:neuronunit} do not exhaust the possible sources of models, capabilities, and test data, they provide an immediate point of entry into the neurophysiology community and a powerful demonstration of our proposal. 
In the \textit{NeuronUnit} repository (\url{http://github.com/scidash/neuronunit}) is a runnable script (\textit{examples.py}) demonstrating a complete testing pipeline. 
It (1) selects an OSB model; 
(2) simulates it using NeuroConstruct; 
(3) tests the widths of the resulting action potentials, extracted and computed using NeuroTools, against NeuroElectro data downloaded on-the-fly, using a \textit{NeuronUnit} test class called \verbx{SpikeWidthTest}; 
and (4) computes and prints a test score (Figure~\ref{fig:neuronunit_example}).
